A self-consistency check for unitary propagation of Hawking quanta

### 2017-03-01 Draft_BH_shells.tex

One might object that the Eq.~(\ref{eq-stdcls}) is not entirely classical, since the value of $\Delta y^{\rm ds}$ has to originate from the unknown quantum mechanics of the double-slit. 
This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}). 
Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit. 
Namely, its value should be fixed if we move the screen further away. Eq.~(\ref{eq-stdcls}) shows that with a fixed $\Delta y^{\rm ds}$, we can always make $L$ large enough to satisfy this condition. 
Thus, at least at the level of gedanken experiment, one can always arrange a situation that the interference pattern is visible and subsystem unitarity is valid.

@@

We thank Raphael Bousso, Pei-Ming Ho and Robert Jefferson for discussions. 
This work is supported by the Canadian Government through the Canadian Institute for Advance Research and Industry Canada, 
and by Province of Ontario through the Ministry of Research and Innovation. 
The Dunlap Institute is funded through an endowment established by the David Dunlap family and the University of Toronto.

>>>>

In other words, we have proven the following statement:
{\it If we do not see an interference pattern because the quantum uncertainty of the double-slit position is too large and it makes the pattern blurry, then the evolution for the particle alone is not unitarity, because it becomes entangled with the double-slit.}

One might object that the Eq.~(\ref{eq-stdcls}) is not entirely classical, since the value of $\Delta y^{\rm ds}$ has to originate from the unknown quantum mechanics of the double-slit.
Thus, within a classical theory, even if we do not see an interference pattern, we can never know whether $\Delta y^{\rm ds}$ is the true reason that erases the interference pattern.
This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}). 
Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit and has a finite value.
Namely, its value should be fixed if we move the screen.
Therefore, there will be a distance too close, such that Eq.~(\ref{eq-stdcls}) is not satisfied, and unitarity of the particle is lost.
There will also be a distance far enough, such that Eq.~(\ref{eq-stdcls}) is satisfied, and the subsystem unitarity for the particle is valid.
At the level of gedanken experiment, we would always want to make sure that the second case is true.

@@

We thank Raphael Bousso, Steffen Gielen, Pei-Ming Ho and Robert Jefferson for discussions. 
This work is supported by the Canadian Government through the Canadian Institute for Advance Research and Industry Canada, 
and by Province of Ontario through the Ministry of Research and Innovation. 
The Dunlap Institute is funded through an endowment established by the David Dunlap family and the University of Toronto.
